---
title: "R Markdown Shortcut"
author: "Kaining Zhou"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
setwd("C:/Users/Kaining/BGU ZKN/R/RMarkdown/Tips")
```

#### **1. Prerequisites (chapter 12)**

* Registered a free GitHub account (chapter 4).
* Installed/updated R and RStudio (chapter 5).
* Installed Git (chapter 6).
* Introduced yourself to Git (chapter 7).
* Confirmed that you can push to / pull from GitHub from the command line (chapter 9).

<p>&nbsp;</p>

#### **2. Make a repo on GitHub**

Go to https://github.com and make sure you are logged in.

On your own profile page, click on **“Repositories”**, then click the green **“New”** button.

Then to fill like this:

* Repository name: myrepo (or whatever you wish, we’ll delete this soon anyway).
* Description: “testing my setup” (or whatever, but some text is good for the README).
* Public.
* Initialize this repository with a README.

For everything else, just accept the default.

Click big green button **“Create repository.”**

Click the green **“Code”** button, then copy the HTTPS clone URL to your clipboard 

<p>&nbsp;</p>
#### **3. Clone the repo to your local computer**

In RStudio, start a new Project:

* **File** > **New Project** > **Version Control** > **Git**. In **“Repository URL”**, paste the URL of your new GitHub repository. It will be something like this https://github.com/Kaining26/myrepo.git.
Accept the default project directory name, e.g. myrepo, which coincides with the GitHub repo name.

* Take charge of where the Project will be saved locally. A commonmistake is to have no idea where you are saving files or what your working directory is. 

* Check **“Open in new session”**. 
* Click **“Create Project”**.
You should find yourself in a new local RStudio Project that represents the new test repo we just created on GitHub.

<p>&nbsp;</p>
#### **4. Push your local changes online to GitHub**
Go to the shell. In RStudio, **Tools** > **Shell** 

Type these command lines one by one:

* git add -A
* git commit -m "A commit from my local computer"
* git push

<p>&nbsp;</p>
#### **5. Confirm the local change propagated to the GitHub remote**

Go back to the browser. Reload the Github webpage.You should see all your local files of this project being uploaded to the repo.

<p>&nbsp;</p>
#### **6. How if changes are made from Github and you want to sync in your local computer (chapter 15) **

* Assume you add *“Line added from GitHub”* in Github and commit changes.

* Back to local RStudio. Inspect your README.md. It should NOT have the line *“Line added from GitHub”*.

* Click the **Pull** button at the upper right panel.

* Look at README.md again. You should now see the new line there.

<p>&nbsp;</p>
#### **Reference: Happy Git and GitHub for the useR**
https://happygitwithr.com/

